---
title: "Gambling And Crime"
# subtitle: "<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
subtitle: "A Diff-in-Diff Experiment"
author: "Pengfei Qin, Yuling Wu, Zhichao Shan"
date: "May 23 2021"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---

```{css, echo=FALSE}
# CSS for including pauses in printed PDF output (see bottom of lecture)
@media print {
  .has-continuation {
    display: block !important;
  }
}
```

```{r setup, include=FALSE}
# xaringanExtra::use_scribble() ## Draw on slides. Requires dev version of xaringanExtra.

options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=4, #fig.width=6,
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=T#, echo=F, warning=F, message=F
  )
library(tidyverse)
library(hrbrthemes)
library(fontawesome)

```



```{r, echo=FALSE}
library(pacman)
p_load(readr,dplyr,stargazer,sandwich,tidyverse,broom)

```


```{r, echo=FALSE}
#create dummy variable year over 2013
gamble <- read.csv('Gambling_NJ_MI.csv')

gamble <- mutate(gamble, after = ifelse(gamble$Year>=2013, 1, 0))

gamble <- mutate(gamble, treatafter = after*Treat)


treated <- subset(gamble, gamble$Treat==1)
```

```{r, echo=FALSE}
gou <- read.csv('Gambling Or,Utah.csv')

gou <- mutate(gou, after = ifelse(gou$Year>=1985, 1, 0))

gou <- mutate(gou, treatafter = after*Treat)

treated_ou <- subset(gou, gou$Treat==1)
```



```{r, echo=FALSE}
gamble_NJ = gamble %>%
  filter(Treat == 1)

gamble_MI = gamble %>%
  filter(Treat == 0)

gamble_OR = gou %>%
  filter(Treat == 1)

gamble_UT = gou %>%
  filter(Treat == 0)

```



# Introduction



### Topic

- How gambling legalization affect crime in different states.



### Reasons

- Gambling makes people addicted

- Gambling makes people lose their minds

- Gambling makes people bankrupt

- Gambling leads people to crime

---

# Background

### Oregon

- Population : 2586327 (mean from 1970 - 1994)

- Legal time for gambling: 1985

### Utah

- Population : 1490074 (mean from 1970 - 1994)

- Legal time for gambling: 1985

---

# Background

### New Jersey

- Population : 8760109 (mean from 2000 - 2019)

- Legal time for online gambling: 2013

### Michigan

- Population : 1490074 (mean from 2000 - 2019)

- Legal time for online gambling: 2013


---

# Data

### Where

- www.disastercenter.com

### What's in it

- Year, Population, Overall Index, Violent, Property Crime, Murder, Rape, Robbery, Aggravated Assault, Burglary, Larceny Theft, Vehicle Theft

### What variables we used

- For normal gambling, we used Robbery, Property Crime, Theft, Overall Index

- For online gambling, we used Murder, Property Crime, Theft, Overall Index

---

# Method

- Difference-in-Difference

$Crime\ Index = \alpha_0 +\alpha_1*Treat + \alpha_2*After +\alpha_3*TreatAfter + \alpha_4*Year + \alpha_5 * Population + \xi_1$

- We use the data before and after gambling was allowed in Oregon in 1986 and the data before and after in Utah in 1985 to compare. 



- We use the data before and after online gambling was allowed in New Jersey in 2013 and the data before and after in Michigan in 2013 to compare. 



---

# Graph For New Jersey And Michigan



```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_NJ, aes(x = Year, y = Murder, col = "1")) +
  geom_line(data = gamble_MI, aes(x = Year, y = Murder, col = "0")) +
  geom_point(data = gamble_NJ, aes(x = Year, y = Murder, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_MI, aes(x = Year, y = Murder, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 2013, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Murder and Time", x = "Year", y = "Murder") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```

```{r, echo=FALSE}
ge_nmM <- lm(Murder ~ Treat+after+treatafter+Year+Population, data=gamble)
tidy(ge_nmM)
```

---

# Graph For New Jersey And Michigan


```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_NJ, aes(x = Year, y = Property, col = "1")) +
  geom_line(data = gamble_MI, aes(x = Year, y = Property, col = "0")) +
  geom_point(data = gamble_NJ, aes(x = Year, y = Property, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_MI, aes(x = Year, y = Property, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 2013, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Property and Time", x = "Year", y = "Property") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```

```{r, echo=FALSE}
ge_nmP <- lm(Property ~ Treat+after+treatafter+Year+Population, data=gamble)
tidy(ge_nmP)
```

---

# Graph For New Jersey And Michigan


```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_NJ, aes(x = Year, y = Larcency_Theft, col = "1")) +
  geom_line(data = gamble_MI, aes(x = Year, y = Larcency_Theft, col = "0")) +
  geom_point(data = gamble_NJ, aes(x = Year, y = Larcency_Theft, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_MI, aes(x = Year, y = Larcency_Theft, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 2013, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Larceny Theft and Time", x = "Year", y = "Larceny Theft") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```

```{r, echo=FALSE}
ge_nmT <- lm(Larcency_Theft ~ Treat+after+treatafter+Year+Population, data=gamble)
tidy(ge_nmT)
```

---

# Graph For New Jersey And Michigan


```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_NJ, aes(x = Year, y = Index, col = "1")) +
  geom_line(data = gamble_MI, aes(x = Year, y = Index, col = "0")) +
  geom_point(data = gamble_NJ, aes(x = Year, y = Index, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_MI, aes(x = Year, y = Index, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 2013, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Overall Crime Index and Time", x = "Year", y = "Overall Crime Index") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```

```{r, echo=FALSE}
ge_index <- lm(Index ~ Treat+after+treatafter+Year+Population, data=gamble)
tidy(ge_index)
```

---

# Graph For Oregon And Utah



```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_OR, aes(x = Year, y = Robbery, col = "1")) +
  geom_line(data = gamble_UT, aes(x = Year, y = Robbery, col = "0")) +
  geom_point(data = gamble_OR, aes(x = Year, y = Robbery, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_UT, aes(x = Year, y = Robbery, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 1985, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Robbery and Time", x = "Year", y = "Robbery") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```

```{r,echo=FALSE}
ge_ouR <- lm(Robbery ~ Treat+after+treatafter+Year+Population, data=gou)
tidy(ge_ouR)
```

---

# Graph For Oregon And Utah

```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_OR, aes(x = Year, y = Property, col = "1")) +
  geom_line(data = gamble_UT, aes(x = Year, y = Property, col = "0")) +
  geom_point(data = gamble_OR, aes(x = Year, y = Property, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_UT, aes(x = Year, y = Property, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 1985, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Property and Time", x = "Year", y = "Property") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```

```{r, echo=FALSE}
ge_nmP <- lm(Property ~ Treat+after+treatafter+Year+Population, data=gamble)
tidy(ge_nmP)
```

---

# Graph For Oregon And Utah

```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_OR, aes(x = Year, y = Larceny_Theft, col = "1")) +
  geom_line(data = gamble_UT, aes(x = Year, y = Larceny_Theft, col = "0")) +
  geom_point(data = gamble_OR, aes(x = Year, y = Larceny_Theft, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_UT, aes(x = Year, y = Larceny_Theft, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 1985, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Larceny Theft and Time", x = "Year", y = "Larceny Theft") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```

```{r, echo=FALSE}
ge_ouT <- lm(Larceny_Theft ~ Treat+after+treatafter+Year+Population, data=gou)
tidy(ge_ouT)
```

---

# Graph For Oregon And Utah

```{r, echo=FALSE, warning=FALSE, out.width='70%'}
colors <- c("1" = "#03A9F4", "0" = "black")

ggplot() +
  geom_line(data = gamble_OR, aes(x = Year, y = Index, col = "1")) +
  geom_line(data = gamble_UT, aes(x = Year, y = Index, col = "0")) +
  geom_point(data = gamble_OR, aes(x = Year, y = Index, col = "1", size = 1), show_guide = FALSE) +
  geom_point(data = gamble_UT, aes(x = Year, y = Index, col = "0", size =1), show_guide = FALSE) +
  theme_classic(base_size=8) +
  geom_vline(xintercept = 1985, lty = 4) + 
  scale_color_manual(values = colors) +
  labs(title = "Overall Crime Index and Time", x = "Year", y = "Overall Crime Index") +
  guides(col=guide_legend("Treat")) +
  theme(plot.title = element_text(color = "black", size = 15),
        axis.title = element_text(colour='black', size = 15),
        axis.text = element_text(size = 15),
        legend.position = "top",
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
```
```{r, echo=FALSE}
ge_ouI <- lm(Index ~ Treat+after+treatafter+Year+Population, data=gou)
tidy(ge_ouI)
```


---

# Conclusion

### First Experiment

- Treatment effect for overall crime index after the legalization of online gambling in New Jersey is 286.43.

- Statistically significant

- The legalization of online gambling will increase the crime rate.

### Second Experiment

- Treatment effect for overall crime index after the legalization of ambling in Oregon is -283.43.

- Not Statistically significant

- The legalization of offline gambling will decrease the crime rate.




